Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-02-23 WholePlotTrajectories.Rmd
Manuscript update & DB remove (.gitignore)

Except for leaves cholorphyll content, which displayed higher difference between plots than among treatments which may be due to the completeness of dataset, all CWM trajectories corresponded to significant changes after disturbance.
All functional traits and seed mass proportions displayed a unimodal trajectories but with different times at maximum and different values at the end of the experiment (30 years after disturbance). 
30 years after disturbance, the weighted means of communities specific maximum height at adult stage (Hmax), leaf toughness (L_toughness)and wood specific gravity (WD) remained significantly lower than their initial value and than these of the control plots \@ref(fig:Fig3).
The weighted means of bark thickness (Bark_thick) similarly remained substantilly higher than initially for all disturbed plots while the specfic leaf area (SLA) had almost recovered its initial value and this of the undisturbed plots at the end of the experiment.

>>>>

Except for leaves cholorphyll content, which displayed higher difference between plots than among treatments which may be due to the completeness of dataset, all CWM trajectories corresponded to significant changes after disturbance.
All functional traits and seed mass proportions displayed a unimodal trajectories but with different times at maximum and different values at the end of the experiment (30 years after disturbance). 
30 years after disturbance, the weighted means of communities specific maximum height at adult stage (*Hmax*), leaf toughness (*L_toughness*) and wood specific gravity (*WD*) remained significantly lower than their initial value and than these of the control plots \@ref(fig:Fig3).
The weighted means of bark thickness (*Bark_thick*) similarly remained substantilly higher than initially for all disturbed plots while the specfic leaf area (*SLA*) had almost recovered its initial value and this of the undisturbed plots at the end of the experiment.
